\chapter*{Math}

\section*{\underline{IMPORTS}}

\section*{\underline{DESCRIPTIONS}}
\subsection*{MODULE : Math}
\hypertarget{ecldoc:Math_Math}{}
\begin{enumerate}
\item \hyperlink{ecldoc:Math_math.infinity}{Infinity}
\item \hyperlink{ecldoc:Math_math.nan}{NaN}
\item \hyperlink{ecldoc:Math_math.isinfinite}{isInfinite}
\item \hyperlink{ecldoc:Math_math.isnan}{isNaN}
\item \hyperlink{ecldoc:Math_math.isfinite}{isFinite}
\item \hyperlink{ecldoc:Math_math.fmod}{FMod}
\item \hyperlink{ecldoc:Math_math.fmatch}{FMatch}
\end{enumerate}
\subsection*{ATTRIBUTE : REAL8 Infinity}
\hypertarget{ecldoc:Math_math.infinity}{}
Return a real ''infinity'' value. \\
\subsection*{ATTRIBUTE : REAL8 NaN}
\hypertarget{ecldoc:Math_math.nan}{}
Return a non-signalling NaN (Not a Number)value. \\
\subsection*{FUNCTION : BOOLEAN isInfinite(REAL8 val)}
\hypertarget{ecldoc:Math_math.isinfinite}{}
Return whether a real value is infinite (positive or negative). \\
\textbf{Parameter} : val ||| The value to test. \\
\subsection*{FUNCTION : BOOLEAN isNaN(REAL8 val)}
\hypertarget{ecldoc:Math_math.isnan}{}
Return whether a real value is a NaN (not a number) value. \\
\textbf{Parameter} : val ||| The value to test. \\
\subsection*{FUNCTION : BOOLEAN isFinite(REAL8 val)}
\hypertarget{ecldoc:Math_math.isfinite}{}
Return whether a real value is a valid value (neither infinite not NaN). \\
\textbf{Parameter} : val ||| The value to test. \\
\subsection*{FUNCTION : REAL8 FMod(REAL8 numer, REAL8 denom)}
\hypertarget{ecldoc:Math_math.fmod}{}
Returns the floating-point remainder of numer/denom (rounded towards zero). If denom is zero, the result depends on the -fdivideByZero flag: 'zero' or unset: return zero. 'nan': return a non-signalling NaN value 'fail': throw an exception \\
\textbf{Parameter} : numer ||| The numerator. \\
\textbf{Parameter} : denom ||| The numerator. \\
\subsection*{FUNCTION : BOOLEAN FMatch(REAL8 a, REAL8 b, REAL8 epsilon=0.0)}
\hypertarget{ecldoc:Math_math.fmatch}{}
Returns whether two floating point values are the same, within margin of error epsilon. \\
\textbf{Parameter} : a ||| The first value. \\
\textbf{Parameter} : b ||| The second value. \\
\textbf{Parameter} : epsilon ||| The allowable margin of error. \\

